### 2012-06-30 inst/examples/bh_lognormal.Rmd
lognormal noise at sigma=.2, since larger noise crashes stocks
try with nonzero cost

`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="bh_lognormal/", verbose=TRUE or`

@@

``` {r  profit}
price <- 1
c0 <- 0.0
c1 <- 0
profit <- profit_harvest(price=price, c0 = c0, c1=c1) 
````

@@

``` {r runall}
lvl <- 0.5
````

@@

``` {r runallsims, dependson="simfn"} 
policyfn <- list(det=det, low=low, g=g, m=m, i=i, gm=gm, gi=gi, mi=mi, gmi=gmi)
noise <- list( det  = c(0,0,0),        low = c(0.1, .1, .1),  growth = c(lvl, 0, 0),
               measure  = c(0, lvl, 0),implement = c(0,0,lvl),growth_measure = c(lvl, lvl, 0), 
               growth_implement = c(lvl, 0, lvl),  measure_implement = c(0, lvl, lvl), all = c(lvl, lvl, lvl)) 
allcases <- lapply(policyfn, function(policyfn_i){
  lapply(noise, function(noise_i){
    simulatereps(policyfn_i, noise_i[1], noise_i[2], noise_i[3])
  })
})
````

>>>>

`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="bh_lognormal_c0/", verbose=TRUE or`

@@

``` {r  profit}
price <- 1
c0 <- 0.01
c1 <- 0
profit <- profit_harvest(price=price, c0 = c0, c1=c1) 
````

@@

``` {r runall}
lvl <- 0.2
````

@@

``` {r runallsims, dependson="simfn"} 
policyfn <- list(det=det, low=low, g=g, m=m, i=i, gm=gm, gi=gi, mi=mi, gmi=gmi)
noise <- list( det  = c(0,0,0),        low = c(0.1, .1, .1),  gro = c(lvl, 0, 0),
               meas  = c(0, lvl, 0),imp = c(0,0,lvl),gro_meas = c(lvl, lvl, 0), 
               gro_imp = c(lvl, 0, lvl),  meas_imp = c(0, lvl, lvl), all = c(lvl, lvl, lvl)) 
allcases <- lapply(policyfn, function(policyfn_i){
  lapply(noise, function(noise_i){
    simulatereps(policyfn_i, noise_i[1], noise_i[2], noise_i[3])
  })
})
````
